---
title: "Vegetable harvest report - tomatoes"
date: 'Created on `r lubridate::today()`'
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
# Set desired options

knitr::opts_chunk$set(
  echo = FALSE,     # omit code
  warning = FALSE,  # omit warnings
  message = FALSE,  # omit messages
  error = TRUE)     # keep errors but still knit
```

```{r libraries}
# Load packages to access more functions

library(tidyverse)      # for plotting and wrangling data
library(gardenR)        # for Lisa's garden data
library(DT)             # for nice large tables
library(knitr)          # for kable function
library(gt)             # for nice html tables
library(gtExtras)       # for extensions of gt
library(here)           # for good file referencing

# Set main folder
here::i_am("README.md")
```

## 2021 Garden summary {.tabset .tabset-pills}

The tables and graphs below summarize the total harvest amount by vegetable. Tomatoes make up about `r round(harvest_2021 %>% summarize(prop = sum(weight*(vegetable == "tomatoes"))/sum(weight)) %>% pull(prop),3)*100`\% of the total harvest. 

### Table


```{r}
s2 <- 
  harvest_2021 %>% 
  group_by(vegetable) %>% 
  summarize(total_weight_kg = sum(weight)/1000)
  
s2 %>% 
  arrange(-total_weight_kg) %>% 
  gt() %>% 
  cols_label(
    total_weight_kg = "Weight (kg)"
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "darkblue"),
      cell_text(color = "white")
    ),
    locations = cells_body(
      rows = vegetable == "tomatoes"
    )
  ) %>% 
  tab_options(
    container.height = px(300)
  )
```

### Graph

```{r}
g2 <-
  s2 %>% 
  mutate(veggie_color = vegetable == "tomatoes") %>% 
  ggplot(
    aes(x = total_weight_kg,
        y = fct_reorder(vegetable, total_weight_kg),
        fill = veggie_color)
  ) +
  geom_col(width = .6, 
           show.legend = FALSE) +
  scale_fill_manual(values = c("TRUE" = "darkblue", "FALSE" = "gray")) +
  labs(title = "Total harvest weight (kg) broken out by vegetable",
       x = "",
       y = "") +
  scale_x_continuous(expand = expansion(mult = 0)) +
  theme_minimal() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title.position = "plot",
        axis.text.y = element_text(size = 8))

g2
```

## Tomato harvest 2021 {.tabset .tabset-pills}

```{r}
tomatoes <- 
  harvest_2021 %>% 
  filter(vegetable == "tomatoes")

variety_smry <- tomatoes %>% 
  group_by(variety) %>% 
  summarize(`# of harvests` = n(),
            `Kilograms` = sum(weight)/1000)
```

Of the `r length(unique(tomatoes$variety))` varieties of tomatoes, `r variety_smry %>% arrange(-Kilograms) %>% slice(1) %>% pull(variety)` had the largest harvest. 

### Table

```{r}
variety_smry %>% 
  arrange(-Kilograms) %>% 
  kable(align = "lcc", 
        digits = c(0,0,1))
```


### Graph

```{r}
variety_smry %>% 
  ggplot(
    aes(y = fct_reorder(variety, Kilograms, sum),
        x = Kilograms)
  ) +
  geom_col(fill = "darkblue", 
           width = .6) +
  labs(title = "Total tomato harvest of each variety (kg), 2021",
       x = "",
       y = "") +
  scale_x_continuous(expand = expansion(mult = 0)) +
  theme_minimal() +
  theme(panel.grid = element_blank())
```

##

```{r}
tomatoes %>% 
  group_by(date) %>% 
  summarize(day_harvest = sum(weight)) %>% 
  mutate(cum_harvest = cumsum(day_harvest)) %>% 
  ggplot(
    aes(x = date,
        y = cum_harvest/1000)
    ) +
  geom_point(color = "darkblue") +
  geom_line(color = "darkblue") +
  labs(title = "Cumulative harvest of tomatoes",
       x = "",
       y = "") +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot")
```

